NHF1 Deamination Anchored Excision Site Figure Generation

### 2022-06-15 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

expansionOffset = 10
cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}

threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}
```

```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r read_sequence_enrichment_data}
threePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
                                         rep2 = CPDTimepoints)
for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredCPDEnrichment[[i]])) {
    threePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
                                        rep2 = CPDTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDEnrichment[[i]])) {
    fivePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}

threePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
                                             rep2 = sixFourTimepoints)
for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredSixFourEnrichment[[i]])) {
    threePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
                                            rep2 = sixFourTimepoints)
for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredSixFourEnrichment[[i]])) {
    fivePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 9}
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))

plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep1,
                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep2,
                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
```

```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 9}
plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep2,
                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))

plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep1,
                       title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep2,
                       title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
```

@@

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
                                      rep2 = CPDTimepoints)
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
    threePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
                                     rep2 = CPDTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
    fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}

>>>>

expansionOffset = 10
cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
repNames = c("rep1", "rep2", "all_reps")

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}

threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}
```

```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                 secondaryYAxisLabel = "5' Cut Site Distance",
                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset)
}

for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset)
}
```

```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset)
}

for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset)
}
```

```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq[[i]], 
                                 title = paste(c("6-4", titleCaseFiltering,
                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                 secondaryYAxisLabel = "5' Cut Site Distance",
                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset)
}

for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq[[i]], 
                                 title = paste(c("6-4", titleCaseFiltering,
                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset)
}
```

```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq[[i]], 
                                 title = paste(c("6-4", titleCaseFiltering,
                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset)
}

for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq[[i]], 
                                 title = paste(c("6-4", titleCaseFiltering,
                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset)
}
```

```{r read_sequence_enrichment_data}
threePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredCPDEnrichment[[i]])) {
    threePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDEnrichment[[i]])) {
    fivePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}

threePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints,
                                             all_reps = sixFourTimepoints)
for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredSixFourEnrichment[[i]])) {
    threePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints,
                                            all_reps = sixFourTimepoints)
for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredSixFourEnrichment[[i]])) {
    fivePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
  plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment[[i]],
                         title = paste(c("CPD", titleCaseFiltering,
                                         "3' Anchored YR Enrichment", repNames[i]), collapse = ' '),
                         secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                         expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
}

for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
  plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment[[i]],
                         title = paste(c("CPD", titleCaseFiltering,
                                         "5' Anchored TGG Enrichment", repNames[i]), collapse = ' '),
                         secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                         expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
}
```

```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
  plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment[[i]],
                         title = paste(c("6-4", titleCaseFiltering,
                                         "3' Anchored YR Enrichment", repNames[i]), collapse = ' '),
                         secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                         expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
}

for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
  plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment[[i]],
                         title = paste(c("6-4", titleCaseFiltering,
                                         "5' Anchored TGG Enrichment", repNames[i]), collapse = ' '),
                         secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                         expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
}
```

@@

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
    threePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
    fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
